---
title: "Climate suitability assessment for *`r params$pest.name`* based on the Köppen–Geiger climate classification"
author: "`r params$author.list`"
date: "`r Sys.Date()`<br><br>"
output: html_document
  # officedown::rdocx_document:
  # reference_docx: draft-styles2.docx
params:
  pest.name: "Default pest"
  author.list: "Default author"
---

```{r setup, echo=FALSE}
# setup knitr
knitr::opts_chunk$set(echo = TRUE,
                      dev = c('jpeg'),
                      fig.align = 'center', fig.height = 7, fig.width = 10)
# library(officedown)
# library(officer)

```

Climate suitability based on the Köppen–Geiger climate classification is a relatively simple and easily accessible tool that can simplify and speed-up urgent analysis. This approach identifies areas with the same climates of the areas where a specific organism is distributed. It is a good compromise for simplified assessment with time constraints.<br>

```{r pest-info, echo=FALSE, warning=FALSE, message=FALSE, fig.keep='all'}

# # download EPPO host list table (if selected in configuration file)
# if(i.eppo.host.table=="yes") 
# {
#   source("R_scripts\\PEST.PROFILE.web.EPPO.host.table.r", local = knitr::knit_global())
# }
# Function to create administrative units layers: 
# - create layers including administrative units where pest was observed
# - list of administrative units that were not found due to spelling mistakes, different naming conventions, different enconding, etc...
source("R_scripts\\_PEST.PROFILE.admin.layer.fun.r", local = knitr::knit_global())
# Function to extract climates from complete Koppen-Geiger map for the administrative units or points where pest was observed
source("R_scripts\\_PEST.PROFILE.extract.climate.fun.r", local = knitr::knit_global())
# load GIS layers
source("R_scripts\\PEST.PROFILE.generate.observations.layers.r", local = knitr::knit_global())
```


```{r DistrLocToBeCheched, echo=FALSE, eval=(length(units.na.list)>0), results='asis'}
cat(
   '### Observed distribution: location names that need to be checked
Please check the following location names that were not recognised by the system:<br>', 
sep="")

cat(units.na.list, sep="<br>")

cat("<br>", sep="")
```

### Observed distribution table<br>

```{r process-map, echo=FALSE, warning=FALSE, message=FALSE, fig.keep='all'}
if(distr.table == TRUE)
{
  # print table including observed distribution (EPPO or user-defined)
  obs.table.show <- pest.kg.table[,c("Continent","Country","State","Observation", "admin.level","admin.source", "lat", "long")]
  colnames(obs.table.show) <- c("Continent","Country","State","Location", "Admin level", "Admin source", "Lat", "Long")
  knitr::kable(obs.table.show, format="pipe", digits = 4)
}

# if protected zone mapping is requested then related layers are loaded
# load list of protected zones
# if(i.include.protected.zones == "yes")
# {
#   source("R_scripts\\PEST.PROFILE.load.protected.zones.r", local = knitr::knit_global())
#   source("R_scripts\\PEST.PROFILE.generate.pz.layers.r", local = knitr::knit_global())
# }
# Extract the list of climates relevant for the pest (RESOURCE DEMANDING)
source("R_scripts\\PEST.PROFILE.extract.list.pest.climates.r", local = knitr::knit_global())
kg.climate.list <- read.csv(paste0(support.info, "KG_climates.csv"), header = TRUE, stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM")

```

<!---BLOCK_LANDSCAPE_START--->
### Climates included in the assessment<br>

```{r pest.climate.table, echo=FALSE, warning=FALSE, message=FALSE, fig.keep='all'}
pest.climate.table <- kg.climate.list[which(kg.climate.list$Climate.code %in% pest.climates.list),]
#rm(kg.climate.list)
knitr::kable(pest.climate.table, format="pipe", row.names = FALSE)
#kable_styling(kbl(pest.climate.table, format="pipe", row.names = FALSE))
```
 <!---BLOCK_LANDSCAPE_STOP--->

<!---BLOCK_LANDSCAPE_START--->
```{r kg-map, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.keep='all'}
# KG pest map (RESOURCE DEMANDING)
source("R_scripts\\PEST.PROFILE.KG.pest.map.R")
 
```
 <!---BLOCK_LANDSCAPE_STOP--->


